Project Glass 2.0 -- Interaction with Physical Devices through Attention

### 2013-05-03 doc/report/main.tex
some minor change

\begin{abstract}
With the increasing interest of assigning intelligence to everyday object, many approaches of interacting with them fall back to smartphone based applications. We argue about the inconvenience, overhead, and distraction in such an interaction paradigm, and propose a more natural solution. A glass-based controller which enables user to express their interest in interaction directly simplifies the process of selection in a smart-home or smart-office senario. We present our thoughts, design and evaluation of such a system in this paper to motivate researchers in considering ``interaction in attention''. In the meantime, we noticed that Google Glass might serve as the perfect enabling technology, though in our prototype we've adopted simple infrared approach for proof-of-concept.
\end{abstract}

>>>>

\begin{abstract}
With the increasing interest of assigning intelligence to everyday object, many approaches of interacting with them fall back to smartphone based applications. We argue about the inconvenience, overhead, and distraction in such an interaction paradigm, and propose a more natural solution. A glass-based controller which enables user to express their interest in interaction directly simplifies the process of selection in a smart-home or smart-office senario. We present our thoughts, design and evaluation of such a system in this paper to motivate researchers in considering ``interaction in attention''. In the meantime, we noticed that Google Glass might serve as the perfect enabling technology, though in our prototype we've adopted infrared approach for proof-of-concept. The evaluation and discussion of such system might be valuable for future work to explore on more mature hardware platform.
\end{abstract}
